### 2016-07-25 correctness.tex
revamping section on trivial attacks

In this experiment we track the time-complexity (relative to some
implied model of computation) and query-complexity (i.e., number of
queries) of the adversary~$A$.  
We define the advantage of adversary~$A$ in the correctness experiment as 
\[
\AdvCorrect{\Pi,\distr{\calS}{},r}{A} = \Prob{\ExpCorrect{\Pi,\distr{\calS}{}, r,}{A}}.
\]
and, overloading notation, we write $\AdvCorrect{\Pi,\distr{\calS}{},r}{t,q}$ for the maximum over all~$t$-time adversaries that ask at most~$q$ queries. Roughly, we say that a
set-representation~$\Pi$ is $(t,q,r,\epsilon')$-correct if $\AdvCorrect{\Pi,\distr{\calS}{},r}{t,q} \leq \epsilon'$.

>>>>

In this experiment we track the time-complexity (relative to some
implied model of computation) and query-complexity (i.e., number of
queries) of the adversary~$A$.  
We define the advantage of adversary~$A$ in the correctness experiment as 
$\AdvCorrect{\Pi,\distr{\calS}{},r}{A} = \Prob{\ExpCorrect{\Pi,\distr{\calS}{}, r,}{A}=1}$.
Overloading notation, we write $\AdvCorrect{\Pi,\distr{\calS}{},r}{t,q}$ for the maximum over all~$t$-time adversaries that ask at most~$q$ queries. Roughly, we say that a
set-representation~$\Pi$ is $(t,q,r,\epsilon')$-correct if $\AdvCorrect{\Pi,\distr{\calS}{},r}{t,q} \leq \epsilon'$.
